Balsa: A Compact Line Notation Based on SMILES

### 2022-08-03 manuscript.tex
Adds intro to Implementation. Closes #47

>>>>

Although Balsa is a simple language at its core, a number of factors can complicate implementation. Some points may be apparent from the description of syntax and semantics, but others may not be visible at such close range. As an aid to software quality, the following section addresses common issues that arise during the development of software to read and/or write Balsa strings.
